---
output: github_document
---

<!-- README.md is generated from README.Rmd. Please edit that file -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%"
)
```

# rlstats


<!-- badges: start -->
<!-- badges: end -->

## Installation

You can install the development version of rlstats from
[GitHub](https://github.com/) with:

``` r
#install.packages("remotes")
#install.packages("devtools")
devtools::install_github("ADC-405-S26/rlstats")
```

**Note: If you're reading this on the Github source code page, there will be a lot of css jargon that it displays. Scroll past to see the table output.**

## Examples

This package contains three main functions. Two for analyzing a specific player, and one for comparison between teams in a match. Below you'll see usage of all three.

```{r example}
library(rlstats)
```


#### stats_for_player

This function outputs a table with some basic summary statistics for a specified player

```{r}
stats_for_player(TDMZ443games, name = "TDMZ443")
```

If your dataset contains data from several games, the above function call will return aggregated statistics for all those games. If you want to specify a particular game, you pass in its match guid.

```{r}
stats_for_player(TDMZ443games, name = "TDMZ443", game = '8DF7C4C211F1560E0ED84EA271D83282')
```


#### speed_boost_plots

This function returns two plots displaying boost total and speed information for a specified player throughout the course of a specified game

```{r}
speed_boost_plots(TDMZ443games, name = 'TDMZ443', game = '8DF7C4C211F1560E0ED84EA271D83282')
```


#### compare_teams

This functions outputs a table with some summary statistics allowing comparison between the performance of both teams in specified match

```{r}
compare_teams(TDMZ443games, '8DF7C4C211F1560E0ED84EA271D83282')
```
