---
title: "Introduction to rlstats"
output: rmarkdown::html_vignette
vignette: >
  %\VignetteIndexEntry{Introduction to rlstats}
  %\VignetteEngine{knitr::rmarkdown}
  %\VignetteEncoding{UTF-8}
---

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>"
)
```

The goal of the `rlstats` is to package is to provide some useful functions for analyzing rocket league gameplay data. A lot of people take Rocket League very seriously from a competitive point of view. Several people seek out and pay for coaching to analyze their gameplay in an attempt to improve. This package may be used by a player or coach to get a more in depth look in to some aspects of a player's gameplay which may be hard to keep track of manually. Especially things like average speed and boost habits. The usage of this package for this purpose requires a player personal gameplay data. If you're interested in using this package, first check out the "Getting your dataset" vignette for instructions on getting your own data.


To install this package through Github, use 

``` r
#install.packages("remotes")
#install.packages("devtools")
devtools::install_github("ADC-405-S26/rlstats")
```
Then load it with the following code -

```{r setup}
library(rlstats)
```


This package currently contains three functions

* `stats_for_player` - gives some basic summary statistics for a specific player
* `speed_boost_plots` - give boost and speed line plots for a specific player in a specific ga,e
* `compare_teams` - give summary statistics comparing each team in a specific game

#Caution
All these functions can take a \textit{game} argument, and the first two listed above take a \textit{name} argument. Unfortunately with the current setup, if you want to look at a specific player or game, you have to know exactly the player name and match guid. For most this won't be an issue with the player name, but to know the match guid you must actually look at your dataset itself, and manually find the match guid. So if you really want to look back on a specific match, one must note its match guid as soon as the data is recorded. A cleaner system for this will be coming soon.
